Robust DPG stability II

### 2012-03-30 docs/NewBCRobustness_paper/paper.tex
committing start of modifications to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@411 36274a68-8941-4c93-80ef-affaed5139da

%\tableofcontents
\maketitle

@@

@@

The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybrid DG method with locally supported optimal test functions.  For a given operator equation $Au = f$, the ultra-weak formulation is 
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, v \rangle - (u,A^*v) - (f,v)
\]
where $A^*$ is the formal adjoint resulting from integration by parts.

\subsection{Choice of test norm}

Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the

Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the optimal test norm 
\[
\|v\|_{\rm opt} = \sup_{u\in U}\frac{b(u,v)}{\|u\|_U}
\]
If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies $\|u\|_E = \|u\|_U$. The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_V$. The reverse $b(u,v) \leq \|u\|_U\|v\|_V$ is proved by
\[
\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \frac{\|v\|_V}{\|v\|_V} = 1
\]
where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).

The norm $\|v\|_{\rm opt}$ is non-localizable, however - even with discontinuous test functions, solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.  The ``quasi-optimal" test norm is created by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables.

A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.  Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.  The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).  The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.  Numerically, DPG appears to provide a ``pollution-free" method for these problems under a specific regularization of the ``quasi-optimal" test norm \cite{DPG4}.

@@

@@

For convection-diffusion, the quasi-optimal norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.  Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).  As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.  Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.  We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions.

@@

\subsection{Boundary conditions and adjoint stability}

To analyze the robustness of DPG, we note that 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
&= \| u \|^2_{L^2}
\end{align*}
for the specific continuous test functions $\tau$ and $v$ satisfying
\begin{align*}
\div \tau - \beta \cdot \grad v &= g \\
\frac{1}{\epsilon}\tau + \grad v &= f
\end{align*}
with $g=u$ and $f=0$, and with boundary conditions
with boundary conditions
\begin{align}
\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
\end{align}
such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, 
\begin{align*}
\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
\end{align*}
We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.  If we can show $\|\left(\tau, v\right)\|_V \lesssim \| g \|_{L^2}$ for any choice of $g \in L^2$, then, for $g=u$, dividing through by $\|u\|_{L^2}$ gives
\[
\|u\|_{L^2} \lesssim \|u\|_E
\]
which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.  The study of robustness for the DPG method has now been reduced to proving stability estimates for the adjoint problem.

Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.  The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
\]
Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton; however, it is necessary to assume in addition $v=0$ on $\Gamma$ to have 
$$b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \|u\|_{L^2}^2.$$  Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.  The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$. It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.  The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.

We improve upon the result of Demkowicz and Heuer by adopting a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.  Using this, we can prove robust control over $\|u\|_{L^2}$ using the using the unweighted version of the test norm in \cite{DPGrobustness}
\[
\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
\]
This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms 
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
\end{align*}
Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
\begin{align*}
\|u\| &= \|u\|_{L^2} \\
\|\sigma\| &= \|\sigma\|_{L^2}
\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]

@@

\subsubsection{Stability of the adjoint problem (bound from below)}

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align}
%\tau \cdot n = 
- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
v &= 0, \quad x\in \Gamma_+ \label{bc_2}
\end{align}
and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.

Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$. The normal trace $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.

We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega$.  The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
\end{align*}
Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.

\begin{proof}
Define $v_\beta = \beta\cdot \grad v$.  Multiplying the adjoint equation \eqref{adjoint} by $v_\beta$ and integrating over $\Omega$ gives
\[
\|v_\beta\|^2 = -\int_\Omega g v_\beta - \epsilon \int_\Omega \Delta v v_\beta
\]
Note that 
\[
-\int_{\Omega} \beta\cdot \grad v \del v = -\int_{\Omega} \beta\cdot \grad v \div \grad v
\]
Integrating this by parts, we get
\[
-\int_{\Omega} \beta\cdot \grad v \div \grad v = \int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v  - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v
\]
Note that 
\[
\grad (\beta \cdot \grad v) = \grad \beta \cdot \grad v + \beta \cdot \grad \grad v
\]
where $\grad \beta$ and $\grad \grad v$ are understood to be tensors. Then, 
\[
\int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v = \int_{\Omega}(\grad \beta\cdot \grad v) \cdot \grad v + \int_{\Omega}\beta\cdot \grad\grad v \cdot \grad v 
\]
Noting that $\grad v \cdot \grad \grad v = \grad\frac{1}{2}\left(\grad v\cdot \grad v\right)$, if we integrate by parts again, we get
%\[
%\int_{\Omega}\beta\cdot \grad\grad v \cdot \grad v = \frac{1}{2}\int_{\Omega}\beta\cdot \grad(\grad v \cdot \grad v ) = \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) - \frac{1}{2}\int_{\Omega}\div \beta (\grad v \cdot \grad v )
%\]
%Then, we can combine these terms to get
\begin{align*}
-\int_{\Omega}  \del vv_\beta &= - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v + \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) - \frac{1}{2}\int_{\Omega}\div \beta (\grad v \cdot \grad v ) + \int_{\Omega}(\grad \beta\cdot \grad v) \cdot \grad v\\
&= - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v + \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) + \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v
\end{align*}
Finally, substituting this into our adjoint equation multiplied by $v_\beta$, we get
\[
\| v_\beta\|^2 = -\int_{\Omega}g\beta\cdot \grad v +  \epsilon\int_{\Gamma}  \left( -n\cdot \grad v \beta + \frac{1}{2}\beta_n \grad v \right) \cdot \grad v + \epsilon\int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v
\]
%The first term on the RHS can be controlled using Young's inequality. 
The last term can be bounded by our assumption on $\|\grad \beta - \frac{1}{2}\div \beta I\|^2 \leq C$.
\[
\epsilon \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v \leq C\frac{\epsilon}{2} \|\grad v\|^2
\]
For the boundary terms, on $\Gamma_-$, $\grad v\cdot n = 0$, reducing the integrand over the boundary to $\beta_n|\grad v|^2 \leq 0$.  On $\Gamma_+$, $v=0$ implies $\grad v \cdot \tau = 0$, where $\tau$ is a tangential direction.  An orthogonal decomposition yields $\grad v = (\grad v \cdot n) n$, reducing the above to 
\[
 \epsilon\int_{\Gamma}  -\frac{1}{2}|\beta_n| (\grad v \cdot n)^2 \leq 0
\]
leaving us with the estimate
\[
\|v_\beta\|^2 \leq  -\int_{\Omega}g\beta\cdot \grad v + C\frac{\epsilon}{2} \|\grad v\|^2
\]
Since $C=O(1)$, an application of Young's inequality and Lemma 1 complete the estimate.
\end{proof}

\begin{lemma}
\label{lemma_boundary}
Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $v$ satisfy \eqref{adjoint} with $f=g=0$, and arbitrary boundary conditions.  Then, there holds
\[
\|\grad v\| = \frac{1}{\epsilon}\|\tau\| \lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
\]
\end{lemma}
\begin{proof}
We follow \cite{analysisDPG} and \cite{DPGrobustness} in decomposing $\tau$ into $z\in H({\rm curl},\Omega)$ and $\psi\in H^1(\Omega)$ such that
\[
\tau = \left(\epsilon \grad \psi - \beta \psi\right) + \curl z
\]
Specifically, $\psi$ is chosen as the solution to 
\begin{align*}
-\epsilon \Delta \psi + \div \left(\beta \psi\right) &= -\div \tau \\
\epsilon \grad \psi \cdot n - \beta_n \psi - \tau\cdot n &= 0, \quad x\in \Gamma_-\\
\psi &= 0, \quad x\in \Gamma_+ 
\end{align*}
Since $\div \beta = 0$, we satisfy \eqref{a_req}, and can use Lemma 1 (with $f = \frac{1}{\epsilon}\tau$) to bound
\[
\epsilon \|\grad \psi\|^2 + \|\psi \|^2 = \frac{1}{\epsilon}\|\tau\|^2
\]
By the above bound and triangle inequality, 
\[
\|\curl z \| \leq \epsilon \|\grad \psi\| + \|\beta \psi\| + \|\tau\| \lesssim \frac{1}{\sqrt{\epsilon}}\|\tau\|
\]
On the other hand, using the decomposition and boundary conditions directly, we can integrate by parts to arrive at
\begin{align*}
\|\tau\|^2 &= (\tau, \epsilon \grad \psi - \beta \psi + \curl z) = (\tau, \epsilon \grad \psi) - (\tau,\beta \psi) + (\tau,\curl z)  \\
&=(\tau, \epsilon \grad \psi) + \epsilon(\grad v,\beta \psi) - \epsilon(\grad v,\curl z)  \\
&=\epsilon \langle [\tau \cdot n],\psi \rangle - \epsilon  \langle n\cdot \curl z, [v]\rangle = \epsilon \langle [\tau \cdot n],\psi \rangle_{\Gamma_h \setminus \Gamma_+} - \epsilon  \langle n\cdot \curl z, [v]\rangle_{\Gamma_h \cup \Gamma_+}\\
&\lesssim \epsilon \|[\tau \cdot n]\| \|\psi\| + \epsilon \| [v]\|\| n\cdot \curl z \| 
\end{align*}
by definition of the boundary norms on $[\tau\cdot n]$ and $[v]$.

>>>>

\tableofcontents
\maketitle

@@

A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.  Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.  The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).

\textcolor{red}{add bit about residual-based stabilization terms and test functions}

@@

The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybridized DG method with locally supported optimal test functions.  For a given operator equation $Au = f$, the ultra-weak formulation is 
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, v \rangle - (u,A^*v) - (f,v)
\]
where $A^*$ is the formal adjoint resulting from integration by parts.

\subsection{Optimal and quasi-optimal test norms}

Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the norm on $U$ in which DPG is optimal. Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, there is an important canonical choice of test norm for any given variational form.

Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the \textit{optimal test norm} 
\[
\|v\|_{\rm opt} = \sup_{u\in U}\frac{b(u,v)}{\|u\|_U}
\]
If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies $\|u\|_E = \|u\|_U$. The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_V$. The reverse $b(u,v) \leq \|u\|_U\|v\|_V$ is proved by
\[
\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \frac{\|v\|_V}{\|v\|_V} = 1
\]
where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}). This is the ideal test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in that norm.

The norm $\|v\|_{\rm opt}$ is non-localizable, however - the inversion of the inner product corresponding to this norm is global, and solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.  In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norms.  The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.  Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}. Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linearized Stokes equations \cite{Camellia}.

@@

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms 
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
\end{align*}
Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
\begin{align*}
\|u\| &= \|u\|_{L^2} \\
\|\sigma\| &= \|\sigma\|_{L^2}
\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical broken $H^1(\Omega_h) \times H({\rm div},\Omega_h)$ norm 
\[
\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \|v\|_{L^2(\Omega_h)}^2 + \|\grad v\|_{L^2(\Omega_h)}^2  + \|\tau\|_{L^2(\Omega_h)}^2 + \|\div \tau\|_{L^2(\Omega_h)}^2
\]
The exact norms that we will place on $V$ will be determined later.

The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
\end{align*}

@@

For convection-diffusion, the quasi-optimal norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.  Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).  As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.

Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive than approximation test functions using a simple $p$-enriched space for $V$. We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.

@@

\subsection{Adjoint stability}

\textcolor{red}{introduce the three lemmas}
An important relationship is the duality of the energy norm and test norm; for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
\begin{align}
\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
\end{align}
The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.

We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.

\subsubsection{Induced adjoint boundary conditions}

Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.

\textcolor{red}{Explain how energy norm convergence in $\|u\| + \epsilon \|u'\|$ returns bad results, and the need for an $O(1)$ term in the test norm.}

The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
\]
We note that 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
&= \| u \|^2_{L^2}
\end{align*}
for the specific continuous test functions $\tau$ and $v$ satisfying
\begin{align*}
\div \tau - \beta \cdot \grad v &= u \\
\frac{1}{\epsilon}\tau + \grad v &= 0
\end{align*}
with boundary conditions
\begin{align}
\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
\end{align}
Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.  Then, for this specific choice of $\left(\tau, v\right)$, 
\begin{align*}
\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
\end{align*}
If we can show $\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}$ for any choice of $u \in L^2$, dividing through by $\|u\|_{L^2}$ gives
\[
\|u\|_{L^2} \lesssim \|u\|_E
\]
which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.

However, we are unable to prove this in the case of Dirichlet boundary conditions. Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.  The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$. It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.  The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.

We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation. Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
\[
\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
\]
This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.

@@

\subsubsection{Bound from below}
\textcolor{red}{introduce the three lemmas}
With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.  In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
\begin{align}
\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
\end{align}
The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
